### 2016-12-17 Latex/section_wave_cascade_f=0.tex
Article compiled with a Makefile (without figure).

\begin{figure}
\centerline{
\includegraphics[width=8cm]{../Figs/fig_spect_energy_budg_c=100_N=3840}}
\caption{Spectral energy fluxes averaged over a long simulation for $c
= 100$ and $n = 3840$.  The fluxes are nondimensionalized by $\eps$
and plotted versus $k/k_f$.  }
\label{fig_seb}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=8cm]{../Figs/fig_Kolmo_c=20_N=3840}}
\caption{
Third order structure functions involved in the exact Kolmogorov law (\ref{eq_Kolmo}) 
averaged over a long simulation for $c = 20$ and $n = 3840$.
%
The structure functions are normalized by $4 \eps r$.
%
Black thick line, $\mean{ \delta J_L|\delta \uu|^2 } 
+ c^2\mean{\delta u_L(\delta h)^2}$;
light thin line, $c^2\mean{\delta u_L (\delta h)^2}$;
dark thin line, $\mean{\delta J_L |\delta \uu|^2}$.
%
The dotted straight line shows $4 \eps_q r$, 
where $\eps_q$ is the quadratic energy dissipation rate.
}
\label{fig_Kolmo}
\end{figure}

@@

\begin{figure}
\centerline{
\includegraphics[width=8cm]{../Figs/fig_spatiotempspectra_c=20_Nh=3840}}
\caption{Spatio-temporal spectra of KE (dark lines) and APE (light
lines) for $c = 20$ and $n = 3840$ versus $\omega/\omega_l$, where
$\omega_l = c k$.  From the larger to the smaller spectra, $k/\delta k
= 12$, 27, 62, 143, 327, and 746.  }
\label{fig_spatiotemp_spectra}
\end{figure}

@@

\begin{figure}
\centerline{
\includegraphics[width=\halfwidth]{../Figs/fig_Emean_c}
\includegraphics[width=\halfwidth]{../Figs/fig_Emean_resol}
}
\caption{Time- and space-averaged energy 
$\langle h|\uu|^2 + c^2 h^2 \rangle/2$ 
of the statistically stationary flows.
%
In (\textit{a}), the energy is divided by 
$\sqrt{\eps}$ and plotted versus $c$ for 3 resolutions:
$n = 960$, dotted lines; 
$n = 1920$, continuous lines and 
$n = 3840$, dashed lines. 
The cyan curves show the law $C_n \sqrt{\eps L_f c}$, 
with $C_n$ a fit coefficient.
%
In (\textit{b}), the energy is divided by 
$\sqrt{\eps L_f c}$ and plotted versus $n$
for six values of $c$ as indicated in the legend.
}
\label{fig_Evsc}
\end{figure}

@@

\begin{figure}
\centerline{
\includegraphics[width=\halfwidth]{../Figs/fig_spectra_c_Nx=1920_k32}
\includegraphics[width=\halfwidth]{../Figs/fig_spectra_c_Nx=3840_k32}
}
\centerline{
\includegraphics[width=\halfwidth]{../Figs/fig_spectra_c_Nx=1920_k2}
\includegraphics[width=\halfwidth]{../Figs/fig_spectra_c_Nx=3840_k2}
}
\caption{
Compensated energy spectra versus $k/k_f$ for different wave speeds $c$.
%
The spectra are compensated by $k^{-3/2}\sqrt{\varepsilon c} $ 
in (\textit{a,b})
and by $k^{-2}c^{1/3} \eps^{5/9} k_f^{4/9} $ 
in (\textit{c,d}).
%
The resolution is 
$n = 1920$ in (\textit{a,c}) and 
$n = 3840$ in (\textit{b,d}).
%
In (\textit{a,c}), the wave speed goes from 10 to 1000
and 
in (\textit{b,d}) from 10 to 200 
(for the precise values, see figure~\ref{fig_Evstime}).
}
\label{fig_spectra_c}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=8cm]{../Figs/fig_spectra_c=40_nh=7680}}
\caption{Compensated spectra
of total energy (thick black line)
kinetic energy (thin dark line) and
available potential energy (thin light line)
for $c = 40$ and $n = 7680$.}
\label{fig_spectra_c40}
\end{figure}

@@

\begin{figure}
\setlength{\halfwidth}{69mm}
\centerline{
\includegraphics[width=\halfwidth]{../Figs/fig_2Dh_c20}
\hspace{-4mm}
\includegraphics[width=\halfwidth]{../Figs/fig_2Dh_c200}
}
\centerline{
\includegraphics[width=\halfwidth]{../Figs/fig_2Duy_c20}
\hspace{-4mm}
\includegraphics[width=\halfwidth]{../Figs/fig_2Duy_c200}
}
\caption{
Snapshots for $n = 1920$ and two values of the wave speed 
$c= 20$ (\textit{a,c}) and $c= 200$ (\textit{b,d}).
The colors represent the thickness in (\textit{a,b}) and
the $y$-component of the velocity in (\textit{c,d}).
The arrows represent the velocity field.
%
The coordinates are nondimensionalized by the characteristic scale of
the forcing $L_f = 3.57$.  }
\label{fig_phys}
\end{figure}

@@

\begin{figure}
\centerline{
\includegraphics[width=\halfwidth]{../Figs/fig_interm_strfct_ux}
\includegraphics[width=\halfwidth]{../Figs/fig_interm_strfct_uy}
}
\caption{
Compensated fifth-order structure functions $\mean{|\delta u_L|^5}/r$ 
of (\textit{a}) the longitudinal increments and (\textit{b}) the
transverse increments. %
The crosses indicate the range of separation $r$ where the exponent
$\zeta_p$ is computed. %
The dashed lines correspond to the Kolmogorov scaling laws $r^{p/3}$
and $\zeta_p = p/3$.  The wave speed and the resolution are $c = 40$
and $n = 7680$.  }
\label{fig_strfct5}
\end{figure}

@@

\begin{figure}
\centerline{
\includegraphics[width=\halfwidth]{../Figs/fig_interm_ux}
\includegraphics[width=\halfwidth]{../Figs/fig_interm_uy}
}
\caption{
Exponents $\zeta_p$ of the structure functions 
of (\textit{a}) the longitudinal increments 
and (\textit{b}) the transverse increments versus the order $p$.
%
The dashed lines correspond to 
the Kolmogorov scaling laws $r^{p/3}$ and $\zeta_p = p/3$.
The wave speed and the resolution are $c = 40$ and $n = 7680$.
}
\label{fig_interm}
\end{figure}

@@

\begin{figure}
\centerline{
\includegraphics[width=\halfwidth]{../Figs/fig_ratio_strfct}
}
\caption{
Ratio of the structure functions of the velocity increments 
$R_p(r) \equiv \mean{|\delta u_L|^p} / \mean{|\delta u_T|^p}$
for $p = 2,$ 3 and 4.
The dotted straight lines indicate the values computed by the shock model:
$R_2 = 2$, $R_3 = 6\pi/8$ and $R_4 = 8/3$.
%
The wave speed and the resolution are $c = 10$ and $n = 7680$.  }
\label{fig_ratio}
\end{figure}

@@

\begin{figure}
\centerline{
\includegraphics[width=\halfwidth]{../Figs/fig_flatness}
}
\caption{ Flatness of the longitudinal and transverse increments for
$c = 10$ and $n = 7680$. The straight continuous lines indicate the
$r^{-1}$-scaling and the straight dashed line the $r^{-3/2}$-scaling.
The inset shows the ratio $F_T/F_L$ and the corresponding value
computed by the shock model, $F_T/F_L = 1.5$.  }
\label{fig_flatness}
\end{figure}
%
Figure~\ref{fig_flatness} shows the flatness of the longitudinal and
transverse increments, computed from a numerical simulation for $c =
10$ and $n = 7680$.
%
For a Gaussian probability distribution the flatness factor is equal
to 3 whereas the shock model predict flatness factors scaling like
$r^{-1}$.
%
We see that here the flatness factors are much larger than 3, of the
order of $10^3$.
%
Remarkably, they scale approximately as $r^{-1}$ as predicted by the
shock model and the ratio $F_T/F_L$ is very close to the predicted
value 1.5.

>>>>

\begin{figure}
% \centerline{
% \includegraphics[width=8cm]{../Figs/fig_spect_energy_budg_c=100_N=3840}}
\caption{Spectral energy fluxes averaged over a long simulation for $c
= 100$ and $n = 3840$.  The fluxes are nondimensionalized by $\eps$
and plotted versus $k/k_f$.  }
\label{fig_seb}
\end{figure}

@@

\begin{figure}
% \centerline{\includegraphics[width=8cm]{../Figs/fig_Kolmo_c=20_N=3840}}
\caption{
Third order structure functions involved in the exact Kolmogorov law (\ref{eq_Kolmo}) 
averaged over a long simulation for $c = 20$ and $n = 3840$.
%
The structure functions are normalized by $4 \eps r$.
%
Black thick line, $\mean{ \delta J_L|\delta \uu|^2 } 
+ c^2\mean{\delta u_L(\delta h)^2}$;
light thin line, $c^2\mean{\delta u_L (\delta h)^2}$;
dark thin line, $\mean{\delta J_L |\delta \uu|^2}$.
%
The dotted straight line shows $4 \eps_q r$, 
where $\eps_q$ is the quadratic energy dissipation rate.
}
\label{fig_Kolmo}
\end{figure}

@@

\begin{figure}
% \centerline{
% \includegraphics[width=8cm]{../Figs/fig_spatiotempspectra_c=20_Nh=3840}}
\caption{Spatio-temporal spectra of KE (dark lines) and APE (light
lines) for $c = 20$ and $n = 3840$ versus $\omega/\omega_l$, where
$\omega_l = c k$.  From the larger to the smaller spectra, $k/\delta k
= 12$, 27, 62, 143, 327, and 746.  }
\label{fig_spatiotemp_spectra}
\end{figure}

@@

\begin{figure}
% \centerline{
% \includegraphics[width=\halfwidth]{../Figs/fig_Emean_c}
% \includegraphics[width=\halfwidth]{../Figs/fig_Emean_resol}
% }
\caption{Time- and space-averaged energy 
$\langle h|\uu|^2 + c^2 h^2 \rangle/2$ 
of the statistically stationary flows.
%
In (\textit{a}), the energy is divided by 
$\sqrt{\eps}$ and plotted versus $c$ for 3 resolutions:
$n = 960$, dotted lines; 
$n = 1920$, continuous lines and 
$n = 3840$, dashed lines. 
The cyan curves show the law $C_n \sqrt{\eps L_f c}$, 
with $C_n$ a fit coefficient.
%
In (\textit{b}), the energy is divided by 
$\sqrt{\eps L_f c}$ and plotted versus $n$
for six values of $c$ as indicated in the legend.
}
\label{fig_Evsc}
\end{figure}

@@

\begin{figure}
% \centerline{
% \includegraphics[width=\halfwidth]{../Figs/fig_spectra_c_Nx=1920_k32}
% \includegraphics[width=\halfwidth]{../Figs/fig_spectra_c_Nx=3840_k32}
% }
% \centerline{
% \includegraphics[width=\halfwidth]{../Figs/fig_spectra_c_Nx=1920_k2}
% \includegraphics[width=\halfwidth]{../Figs/fig_spectra_c_Nx=3840_k2}
% }
\caption{
Compensated energy spectra versus $k/k_f$ for different wave speeds $c$.
%
The spectra are compensated by $k^{-3/2}\sqrt{\varepsilon c} $ 
in (\textit{a,b})
and by $k^{-2}c^{1/3} \eps^{5/9} k_f^{4/9} $ 
in (\textit{c,d}).
%
The resolution is 
$n = 1920$ in (\textit{a,c}) and 
$n = 3840$ in (\textit{b,d}).
%
In (\textit{a,c}), the wave speed goes from 10 to 1000
and 
in (\textit{b,d}) from 10 to 200 
(for the precise values, see figure~\ref{fig_Evstime}).
}
\label{fig_spectra_c}
\end{figure}

@@

\begin{figure}
% \centerline{\includegraphics[width=8cm]{../Figs/fig_spectra_c=40_nh=7680}}
\caption{Compensated spectra
of total energy (thick black line)
kinetic energy (thin dark line) and
available potential energy (thin light line)
for $c = 40$ and $n = 7680$.}
\label{fig_spectra_c40}
\end{figure}

@@

\begin{figure}
\setlength{\halfwidth}{69mm}
% \centerline{
% \includegraphics[width=\halfwidth]{../Figs/fig_2Dh_c20}
% \hspace{-4mm}
% \includegraphics[width=\halfwidth]{../Figs/fig_2Dh_c200}
% }
% \centerline{
% \includegraphics[width=\halfwidth]{../Figs/fig_2Duy_c20}
% \hspace{-4mm}
% \includegraphics[width=\halfwidth]{../Figs/fig_2Duy_c200}
% }
\caption{
Snapshots for $n = 1920$ and two values of the wave speed 
$c= 20$ (\textit{a,c}) and $c= 200$ (\textit{b,d}).
The colors represent the thickness in (\textit{a,b}) and
the $y$-component of the velocity in (\textit{c,d}).
The arrows represent the velocity field.
%
The coordinates are nondimensionalized by the characteristic scale of
the forcing $L_f = 3.57$.  }
\label{fig_phys}
\end{figure}

@@

\begin{figure}
% \centerline{
% \includegraphics[width=\halfwidth]{../Figs/fig_interm_strfct_ux}
% \includegraphics[width=\halfwidth]{../Figs/fig_interm_strfct_uy}
% }
\caption{
Compensated fifth-order structure functions $\mean{|\delta u_L|^5}/r$ 
of (\textit{a}) the longitudinal increments and (\textit{b}) the
transverse increments. %
The crosses indicate the range of separation $r$ where the exponent
$\zeta_p$ is computed. %
The dashed lines correspond to the Kolmogorov scaling laws $r^{p/3}$
and $\zeta_p = p/3$.  The wave speed and the resolution are $c = 40$
and $n = 7680$.  }
\label{fig_strfct5}
\end{figure}

@@

\begin{figure}
% \centerline{
% \includegraphics[width=\halfwidth]{../Figs/fig_interm_ux}
% \includegraphics[width=\halfwidth]{../Figs/fig_interm_uy}
% }
\caption{
Exponents $\zeta_p$ of the structure functions 
of (\textit{a}) the longitudinal increments 
and (\textit{b}) the transverse increments versus the order $p$.
%
The dashed lines correspond to 
the Kolmogorov scaling laws $r^{p/3}$ and $\zeta_p = p/3$.
The wave speed and the resolution are $c = 40$ and $n = 7680$.
}
\label{fig_interm}
\end{figure}

@@

\begin{figure}
% \centerline{
% \includegraphics[width=\halfwidth]{../Figs/fig_ratio_strfct}
% }
\caption{
Ratio of the structure functions of the velocity increments 
$R_p(r) \equiv \mean{|\delta u_L|^p} / \mean{|\delta u_T|^p}$
for $p = 2,$ 3 and 4.
The dotted straight lines indicate the values computed by the shock model:
$R_2 = 2$, $R_3 = 6\pi/8$ and $R_4 = 8/3$.
%
The wave speed and the resolution are $c = 10$ and $n = 7680$.  }
\label{fig_ratio}
\end{figure}

@@

\begin{figure}
% \centerline{
% \includegraphics[width=\halfwidth]{../Figs/fig_flatness}
% }
\caption{ Flatness of the longitudinal and transverse increments for
$c = 10$ and $n = 7680$. The straight continuous lines indicate the
$r^{-1}$-scaling and the straight dashed line the $r^{-3/2}$-scaling.
The inset shows the ratio $F_T/F_L$ and the corresponding value
computed by the shock model, $F_T/F_L = 1.5$.  }
\label{fig_flatness}
\end{figure}
%
Figure~\ref{fig_flatness} shows the flatness of the longitudinal and
transverse increments, computed from a numerical simulation for $c =
10$ and $n = 7680$.
%
For a Gaussian probability distribution the flatness factor is equal
to 3 whereas the shock model predict flatness factors scaling like
$r^{-1}$.
%
We see that here the flatness factors are much larger than 3, of the
order of $10^3$.
%
Remarkably, they scale approximately as $r^{-1}$ as predicted by the
shock model and the ratio $F_T/F_L$ is very close to the predicted
value 1.5.
